cardinalR: Generating interesting high-dimensional data structures

### 2025-10-03 paper-cardinalR.Rmd
Updated Trefoil table
Removed adding noise dimnsions text

For all branch-generating functions, when the target dimensionality $p > 2$, additional dimensions are filled with independent noise, allowing the $2\text{-}D$ or $2\text{-}D$-subspace structures to be naturally embedded in higher-dimensional space while preserving the intended geometric patterns.

@@

```{r}
trefoil_tb <- tibble(fun = c("gen_trefoil4d",
                            "gen_trefoil3d"), 
                        exp = c("Trefoil in $4\\text{-}D$.",
                                "Trefoil in $3\\text{-}D$."))
```

>>>>

@@

```{r}
trefoil_tb <- tibble(fun = c("gen_trefoil4d",
                            "gen_trefoil3d"), 
                        exp = c("Trefoil in 4-D.",
                                "Trefoil in 3-D."))
```

### 2025-10-03 paper-cardinalR.tex
Updated Trefoil table
Removed adding noise dimnsions text

For all branch-generating functions, when the target dimensionality \(p > 2\), additional dimensions are filled with independent noise, allowing the \(2\text{-}D\) or \(2\text{-}D\)-subspace structures to be naturally embedded in higher-dimensional space while preserving the intended geometric patterns.

@@

\caption{\label{tab:trefoil-tb-pdf}cardinalR trefoil data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_trefoil4d & Trefoil in \$4\textbackslash{}text\{-\}D\$.\\
gen\_trefoil3d & Trefoil in \$3\textbackslash{}text\{-\}D\$.\\
\bottomrule
\end{tabular}
\end{table}

>>>>

@@

\caption{\label{tab:trefoil-tb-pdf}cardinalR trefoil data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_trefoil4d & Trefoil in 4-D.\\
gen\_trefoil3d & Trefoil in 3-D.\\
\bottomrule
\end{tabular}
\end{table}
